Meta-analysis

### 2020-01-19 05_MetaAnalysis.Rmd
Remove yaml header

---
title: "Meta-analysis"
author: "P. Melloy"
date: "`r Sys.Date()`"
output: html_document
---

```{r MEsummary_Libraries, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
# install.packages("lme4")

@@

There seems like no difference between the treatments, with exception to Late_plus. Lets do this plo again, but use the proportion of yield increase compared to the no spray control as the response variable.

>>>>

```{r MEsummary_Libraries1, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
# install.packages("lme4")

@@

There seems like no difference between the treatments, with exception to Late_plus. Lets do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
